Sequence-to-sequence Architecture\\Using BERT

### 2020-06-26 latex/paper/paper.tex
Rearrange the paper and slides folders
Update paper

\usepackage{aaai}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{hyperref}
\usepackage{siunitx}
\sisetup{output-exponent-marker=\ensuremath{\mathrm{e}}}

@@

@@

As we focused our project on automatic email reply, we used The Enron Email Dataset\footnote{\href{https://www.kaggle.com/wcukierski/enron-email-dataset}{https://www.kaggle.com/wcukierski/enron-email-dataset}} to train our model. The dataset contains only the raw data of the emails. Therefore, we created a parser\footnote{\href{https://www.kaggle.com/claudioscheer/extract-reply-emails}{https://www.kaggle.com/claudioscheer/extract-reply-emails}} to extract the email and the replies from the raw data of the email.

To identify whether an email has a reply or not, we look for emails that contain the string \texttt{-----Original Message-----}. After filtering only emails with non-empty replies, we parse those emails in an input sequence (the original email) and in the target sequence (the reply email). The entire extraction was done automatically, that is, we did not manually extract or adjust any email.

We used two libraries to parse the dataset: \texttt{talon}\footnote{\href{https://github.com/mailgun/talon}{https://github.com/mailgun/talon}}, provided by Mailgun, and \texttt{email}, provided by Python. The \texttt{email} package returns the email body with the entire thread. To extract only the last reply from an email thread, we use the \texttt{talon} package.

The original dataset contains \num{517401} raw emails. After parsing the raw dataset, we created a dataset with \num{110205} input and target pairs. As we have limited resources available, we limit the length of emails to \num{256} characters. We ended up with \num{40062} emails with reply in the dataset.

Of that total, we selected \num{10002} emails to train the sequence-to-sequence model. From the rest of the emails, we chose random emails to evaluate the model, as shown in Section~Results.

@@

We use a pre-trained BERT model, provided by Hugging Face\footnote{\href{https://huggingface.co/}{https://huggingface.co/}}. Hugging Face also provides a PyTorch library for using the pre-trained models. Therefore, this library was used to implement the sequence-to-sequence model.

The \texttt{BertModel} class provided by Hugging Face can behave as an encoder or decoder. The difference is that, for the encoder, only a layer of self-attention is used and, for decoder, a layer of cross-attention is added between the layers of self-attention. In a nutshell, the difference is that self-attention is only applied to the input sequence, while cross-attention is applied to the input and output sentences.

we used the bert base

To train the model, we use the following hyperparameters:

\begin{itemize}
    \item Learning rate: \num{3e-5};
    \item Epochs: \num{128};
    \item Adam epsilon: \num{1e-08};
    \item Batch size: \num{8};
    \item Beam search hypothesis: \num{3};
\end{itemize}

% Explanation of warm-up.
% https://datascience.stackexchange.com/questions/55991/in-the-context-of-deep-learning-what-is-training-warmup-steps

The batch size was limited by the amount of memory available on the GPU used to train the model. A TITAN X with 12 GB of memory was used. \num{8} was the highest possible number.

Different values were tested for the learning rate and epochs. We did not change the default value for Adam epsilon. We also tested to accumulate gradients from more than one batch, but did not get good results.

Training the sequence-to-sequence model in less epochs resulted in a model with a lot of noise in the reply email. As we had a limited batch size, increasing epochs increased the training time considerably. Training time is also the reason why the entire dataset was not used. The final model took about \num{6} days to train.

When we increased the learning rate to \num{1e-4}, the model converged faster until the value of the loss function was about \num{2}\footnote{We forgot to capture the loss values over the training epochs. And, as the GPU is shared with other research groups, and we had monopolized the GPU for about three weeks, we were unable to run the experiments again.}. After that point, the loss started to increase and decrease according to the batch. This same behavior is true when using \num{3e-5} as learning rate. However, the difference is that the loss function starts to have this behavior when the loss value is closer to zero.

The last changed hyperparameter was the number of hypothesis explored in each branch of the beam search. We tested a number greater than \num{3}. However, higher values resulted in some words being out of context in the generated reply email.

@@

\bibliographystyle{aaai}
\bibliography{../latex-data/references}

>>>>

\usepackage{aaai}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{hyperref}
\usepackage{siunitx}
\usepackage{graphicx}
\sisetup{output-exponent-marker=\ensuremath{\mathrm{e}}}

@@

discuss it here

In a nutshell, the difference is that self-attention is only applied to the input sequence, while cross-attention is applied to the input and output sentences.

@@

As the project focus is on automatic email reply, The Enron Email Dataset\footnote{\href{https://www.kaggle.com/wcukierski/enron-email-dataset}{https://www.kaggle.com/wcukierski/enron-email-dataset}} was used to train the model. The dataset contains only the emails raw data. Therefore, a parser\footnote{\href{https://www.kaggle.com/claudioscheer/extract-reply-emails}{https://www.kaggle.com/claudioscheer/extract-reply-emails}} was built to extract the email and the replies from the raw data of the email.

To identify whether an email has a reply or not, we look for emails that contain the string \texttt{-----Original Message-----}. After filtering only emails with non-empty replies, those emails were parsed into an input sequence (the original email) and a target sequence (the reply email). The entire extraction was done automatically, that is, we did not extract or adjust any email manually.

Two libraries were used to parse the dataset: \texttt{talon}\footnote{\href{https://github.com/mailgun/talon}{https://github.com/mailgun/talon}}, provided by Mailgun, and \texttt{email}, provided by Python. The \texttt{email} package returns the email body with the entire thread. To extract only the last reply from an email thread, the \texttt{talon} package was used.

The original dataset contains \num{517401} raw emails. After parsing the raw dataset, the new dataset consisted of \num{110205} input and target pairs. As the resources available to fine-tune the model were limited,  only emails with less than \num{256} characters were used. The final dataset consisted of \num{40062} emails. All of these input and target pairs were used to train the BERT model.

@@

A pre-trained BERT model, provided by Hugging Face\footnote{\href{https://huggingface.co/}{https://huggingface.co/}}, was used. Hugging Face also provides a PyTorch library for using the pre-trained models. Therefore, this library was used to implement the sequence-to-sequence model, with PyTorch 1.5.1.

The \texttt{BertModel} class provided by Hugging Face can behave as an encoder or decoder. The difference is that, for the encoder, only a layer of self-attention is used and, for decoder, a layer of cross-attention is added between the layers of self-attention. The difference between these attention mechanisms is discussed in Section~BERT.

In this paper, the BERT base architecture was used. This model uses fewer resources, which allowed us to increase the batch size. To fine-tune the model, the following hyperparameters was used:

\begin{itemize}
    \item Learning rate: \num{1e-4};
    \item Warm-up steps: \num{5000};
    \item Epochs: \num{10.5};
    \item Adam epsilon: \num{1e-4}, same as in the original BERT paper \cite{DBLP:journals/corr/abs-1810-04805};
    \item Batch size: \num{10};
    \item Beam search hypothesis: \num{3};
\end{itemize}

In the fine-tune process, an EC2 spot instance on AWS was used. A checkpoint of the model was saved every \num{20000} steps, mitigating the loss of processment if the instance was suddenly stopped. The instance was equipped with a 16 GB NVIDIA T4 GPU (CUDA 10.2).

The batch size was limited by the amount of GPU memory available. We also tested to accumulate and update the gradients after \num{4} steps, but we did not see any improvements.

Different values were tested for the learning rate and epochs, with and without warm-up. Figure~\ref{fig:learning-rate-schedule} shows the final results of the learning rate update during the fine-tuning process.

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.47\textwidth]{../images/warmup_linear_schedule.pdf}
    \caption{Learning rate schedule}
    \label{fig:learning-rate-schedule}
\end{figure}

Figure~\ref{fig:loss} shows the loss function value over the fine-tuning process. We do not know why, but loss function shows a greater decrease at the end of each epoch.

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.47\textwidth]{../images/loss_function.pdf}
    \caption{Loss function}
    \label{fig:loss}
\end{figure}

Some hyperparameters configuration shows bad results in the loss function. For example:

\begin{itemize}
    \item learning rates greater than \num{1e-4} did not make the model converge;
    \item the use of a warm-up period allowed the model to converge in less epochs;
    \item a high number of epochs almost causes an overfitting of the model;
\end{itemize}

The last changed hyperparameter was the number of hypothesis explored in each branch of the beam search. A number greater than \num{3} resulted in more words being out of context in the generated reply email.

@@

\bibliographystyle{aaai}
\bibliography{references}
